### 2023-04-04 reachable-resilience.tex
a first look at how 4.2 should be changed

\begin{theorem}
{\sc state-resilience} is decidable for WSTS with downward compatibility,
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{theorem}

@@

\begin{proof}
Enumerate the downard-closed sets that contain $s$ and are closed under $\post$.
For ‘each of them’
check
intersection with $\Bad \subseteq \pred^*(\Safe)$.
If $(\downarrow  \post^*(s)) \cap \Bad \subseteq \pred^*(\Safe)$
then we know we will find some 
member of the enumeration such that
subseteq hold;
Conversely
compute

$$ \post(s), ~ \downarrow \post(s), \downarrow \post^2(s) \ldots $$

and ...

check whether at one point we encounter some element in $\Bad$ but not in $\pred^*(\Safe)$.

@@

\mathieu{by symmetry} for downward compatible WSTS:

@@

>>>>

\begin{theorem}
{\sc state-resilience} is decidable for ideal effective WSTS with downward compatibility,
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{theorem}

@@

\begin{proof}

Procedure 1 enumerates inductive invariants in some fixed order $D_1$ , $D_2$ , . . . , i.e. downward closed subsets $D_i \subseteq S$ such that $\downarrow \post(D_i ) \subseteq D_i$. 
Every inductive invariant $D_i$ is an “over-approximation” of $\downarrow \post^*(s)$ if it contains $s$.
Notice that, by standard monotonicity, $\downarrow \post^*(s)$ is such an inductive invariant and may eventually be found.

Procedure 1 stops when it finds an invariant $D$ such that
$D  \cap \Bad \subseteq \pred^*(\Safe)$. 
Indeed
$D  \cap \Bad \subseteq  \pred^*(\Safe)$ implies
$\downarrow \post^*(s) \cap \Bad \subseteq  \pred^*(\Safe)$
since $ \downarrow \post^*(s)  \subseteq D$.

The second procedure iteratively computes
$post^{\leq n}(s) \cap \Bad$
until it finds an element
not in $\pred^*(\Safe)$.
\end{proof}

@@

\mathieu{by symmetry} for downward compatible WSTS (but not necessarily upward compatible):

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & $\emptyset $ & downward compatible & strongly downward compatible  \\ \hline
   SRP & Undecidable  & Decidable   & Decidable \\ \hline
   BSRP & Undecidable  &  ??  & Decidable \\ \hline
      kSRP & Undecidable  & ?? & Decidable  \\ \hline
 \end{tabular}
\end{center}
